---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# totalsummaryfunction

The goal of *totalsummaryfunction* is to allow you to use and understand the function *total_summary*. This will allow you to quickly and easily visualize all the summary stats you might like to know about a given variable in a dataframe. You can choose to group this summary variable by one or more grouping variables, if you would like, or leave out the grouping entirely.

To be specific, the summary statistics output by *total_summary* are the mean, range, minimum, 1st quartile, median, 3rd quartile, and maximum.

## Installation

You can install the development version of *totalsummaryfunction* from [GitHub](https://github.com/) with:

``` r
# install_github("stat545ubc-2024/totalsummaryfunction", ref = "0.1.0")
```

From there, it is the simple matter of loading the package with the *library* function, and you're good to go.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(totalsummaryfunction)

# dataframe for example

data <- data.frame(
  colour = rep(c("Red", "Blue", "Yellow"), each = 5),
  number = rnorm(15))

# quick example

total_summary(data, colour, summ_var = number)

```
